---
title: "The pirate bay analysis"
output: html_document
---

Load data:
```{r}
d <- read.csv('tidy_data/thepiratebay.csv')
str(d)
d$peers <- d$leechers + d$seeders
d$diff <- d$leechers - d$seeders    # not used
d$category <- as.factor(d$category)
d$group <- as.factor(as.numeric(as.character(d$category)) %/% 100)
levels(d$group) <- c("audio", "video", "software", "games", "porn", "other")
```

Order by number of torrents in each group.
```{r, message=F, fig.align="center"}
require(ggplot2)
ordered_d <- within(d, group <- factor(group, levels=names(sort(table(group), decreasing=TRUE))))
ggplot(ordered_d, aes(x = group)) + geom_bar(identity="bar")
```

Overall peers plot:
```{r, fig.align="center"}
a <- aggregate(d$peers, by=list(group=d$group), FUN=mean)
ggplot(a, aes(group, x)) + geom_bar(stat="identity")
```


Aggregate by seeders and leechers and make plots. Count only torrents, with positive number of seeders/leechers.
```{r, fig.align="center"}
a <- aggregate(d$leechers, by=list(group=d$group), FUN=function(x) {x})
a$x <- sapply(a$x, function(x) {ifelse(x > 0, x, NA)})
a$medianLeechers <- sapply(a$x, median, na.rm=T)
ggplot(a, aes(group, medianLeechers)) + geom_bar(stat="identity")

a <- aggregate(d$seeders, by=list(group=d$group), FUN=function(x) {x})
a$x <- sapply(a$x, function(x) {ifelse(x > 0, x, NA)})
a$medianSeeders <- sapply(a$x, median, na.rm=T)
ggplot(a, aes(group, medianSeeders)) + geom_bar(stat="identity")
```


Find statistics for each category:
```{r, warning=F, message=F}
require(XML)
raw_cat_names <- xmlToList("raw_data/categories_names.xml")
nameid <- c(1:length(raw_cat_names))
name <- c(1:length(raw_cat_names))
for (i in 1:length(raw_cat_names))
{
   nameid[i] <- raw_cat_names[i]$option$.attrs
   name[i] <- raw_cat_names[i]$option$text
}
levels(d$category) <- name
```

```{r, results='asis', message=F}
require(knitr)
seeders_and_leechers <- subset(d, select=c("seeders", "leechers"))
amean <- aggregate(x=seeders_and_leechers, list(cat=d$category), mean)
amax <- aggregate(x=seeders_and_leechers, list(cat=d$category), max)
amed <- aggregate(x=seeders_and_leechers, list(cat=d$category), median)
aall <- cbind.data.frame(amed$cat, amed$seeders, amed$leechers, amax$seeders, amax$leechers, amean$seeders, amean$leechers)
names(aall) <- c("category", "med_seeders", "med_leechers", "max_seeders", "max_leechers", "mean_seeders", "mean_leechers")
kable(aall)
```

Find Most popular torrent (for seeders and leechers):
```{r}
# http://thepiratebay.se/torrent/4547709
d[which(d$seeders == max(d$seeders)),]
d[which(d$leechers == max(d$leechers)),]
```


Define function that gets title of torrent by its id.
```{r, message=F}
require(RCurl)
get_title = function(id) {
  url = paste("http://thepiratebay.se/torrent/",id,sep="")
  selector = "//div[@id='title']"
  data = xpathApply(htmlParse(getURL(url)), selector)
  if  (length(data) > 0) {
    rawText = xmlValue(xpathApply(htmlParse(getURL(url)), selector)[[1]])
    gsub("[\n\t]","",rawText)
  } else {
    "Not found"
  }
}
```


```{r}
porn_d <- subset(d, subset=(d$group == "porn"))
popular_porn <- subset(porn_d, subset=(porn_d$peers > 100))
# IMPORTANT: long processing ahead (get_title for more than 1000 torrents)
# popular_porn$title <- sapply(popular_porn$idtorrent, get_title)

# just load data from saved scv
popular_porn <- read.csv('tidy_data/popular_porn.csv')
popular_porn[popular_porn$title == "Not found",]$title = NA
```

There are a lot of NAs in titles:
```{r}
length(which(!is.na(popular_porn$title)))
length(which(!is.na(popular_porn$title))) / length(popular_porn$title)
```

```{r, warning=F, message=F}
require(tm)
corpus <- VCorpus(VectorSource(subset(popular_porn, subset=(!is.na(popular_porn$title)), select=c("title"))))
corpus <- tm_map(corpus, content_transformer(tolower))
corpus <- tm_map(corpus, removeNumbers)
corpus <- tm_map(corpus, removePunctuation)
corpus <- tm_map(corpus, stripWhitespace)
dtm <- DocumentTermMatrix(corpus)
```


Most common words in torrent titles for popular porn (can be genres, actresses or just common terms):
```{r, fig.height=4, fig.width=12, fig.align="center"}
freq <- sort(colSums(as.matrix(dtm)), decreasing=TRUE) # find frequency for each word
words_freq <- data.frame(word=names(freq), freq=freq)
p <- ggplot(subset(words_freq, freq > 5), aes(reorder(word, -freq), freq)) # ordering columns by its frequencies
p <- p + geom_bar(stat="identity")
p <- p + theme(axis.text.x = element_text(angle=45, hjust=1))
p
```

There are sets of popular porn videos (Kamikaze, Barely Legal):
```{r}
titles <- popular_porn$title
titles[grep('kamikaze', titles, ignore.case = T)]
titles[grep('legal', titles, ignore.case = T)]
```

Popular director: Marc Dorcel:
```{r}
titles[grep('dorcel', titles, ignore.case = T)]
```